---
title: "Wing Example Rcpp"
author: "Ambrose Emmett-Iwaniw"
date: "16/8/2023"
output: pdf_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(qrng)
library(Rcpp)
library(parallel)
sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
sourceCpp('C:/Users/arsemmet/Desktop/QR Research/Adaptive_QR_helper.cpp')
source('C:/Users/arsemmet/Desktop/QR Research/sensitivity_analysis.R')
source('C:/Users/arsemmet/Desktop/QR Research/data_preparation.R') 
true_betas = read.csv("C:/Users/arsemmet/Desktop/QR Research/PAPER SIMULATIONS/true_beta_wings.csv")$x
set.seed(20669099)
```

## Data Preparation
```{r DP}
wing_data <- data.frame(matrix(ncol = 10, nrow = 0))
colnames(wing_data) <- c("Sw", "Wfw", "A", "LamCaps", "q", "lam", "tc", "Nz", "Wdg", "Wp")
n <- 2^17
m <- 2^15
d <- 10

U <- interpretable_poly_sets(d,3,8,4)
U = do.call(rbind, U)
```

## WING WEIGHT FUNCTION

```{r}
wingweight <- function(xx)
{
  ##########################################################################
  #
  # WING WEIGHT FUNCTION
  #
  # Authors: Sonja Surjanovic, Simon Fraser University
  #          Derek Bingham, Simon Fraser University
  # Questions/Comments: Please email Derek Bingham at dbingham@stat.sfu.ca.
  #
  # Copyright 2013. Derek Bingham, Simon Fraser University.
  #
  # THERE IS NO WARRANTY, EXPRESS OR IMPLIED. WE DO NOT ASSUME ANY LIABILITY
  # FOR THE USE OF THIS SOFTWARE.  If software is modified to produce
  # derivative works, such modified software should be clearly marked.
  # Additionally, this program is free software; you can redistribute it 
  # and/or modify it under the terms of the GNU General Public License as 
  # published by the Free Software Foundation; version 2.0 of the License. 
  # Accordingly, this program is distributed in the hope that it will be 
  # useful, but WITHOUT ANY WARRANTY; without even the implied warranty 
  # of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the GNU 
  # General Public License for more details.
  #
  # For function details and reference information, see:
  # http://www.sfu.ca/~ssurjano/
  #
  ##########################################################################
  #
  # OUTPUT AND INPUT:
  #
  # y  = wing weight
  # xx = c(Sw, Wfw, A, LamCaps, q, lam, tc, Nz, Wdg, Wp)
  #
  ##########################################################################
  
  Sw      <- 150 + (200-150)*xx[1]
  Wfw     <- 220 + (300-220)*xx[2]
  A       <- 6 + (10-6)*xx[3]
  LamCaps <- (-10 + (10 - -10)*xx[4]) * (pi/180)
  q       <- 16 + (45-16)*xx[5]
  lam     <- 0.5 + (1 - 0.5)*xx[6]
  tc      <- 0.08 + (0.18 - 0.08)*xx[7]
  Nz      <- 2.5 + (6-2.5)*xx[8]
  Wdg     <- 1700 + (2500 - 1700)*xx[9]
  Wp      <- 0.025 + (0.08 - 0.025)*xx[10]
  
  fact1 <- 0.036 * Sw^0.758 * Wfw^0.0035
  fact2 <- (A / ((cos(LamCaps))^2))^0.6
  fact3 <- q^0.006 * lam^0.04
  fact4 <- (100*tc / cos(LamCaps))^(-0.3)
  fact5 <- (Nz*Wdg)^0.49
  
  term1 <- Sw * Wp
  
  y <- fact1*fact2*fact3*fact4*fact5 + term1
  return(y)
}
```


# Why is wing function Sparse?

```{r}
nrow(U)
total_betas = sum(true_betas[-1]^2)
sum(sort(true_betas[-1]^2, decreasing = TRUE)[1:5]) / total_betas
sum(sort(true_betas[-1]^2, decreasing = TRUE)[1:500]) / total_betas
sum(sort(true_betas[-1]^2, decreasing = TRUE)[1:1000]) / total_betas
```

## Code to compute LOF.

```{r}
LOF_EST <- function(d, f, U, betas, gamma=vector(), n=5000){
  Int_sqr_err = rep(NA, n)
  
  if (length(gamma) == 0)
    gamma = rep(1, nrow(U))
  
  X = gen_unif_mat(n, d)
  f_X = sapply(1:n, FUN=function(j){f(X[j,])})
  var_f_x = var(f_X)
  
  for (i in 1:n){
    fi_X_i = 0
    for (j in 1:nrow(U)){
      fi_X_i = fi_X_i + gamma[j]*betas[j]*mulidimensional_basis(U[j,],X[i,])
      }
    Int_sqr_err[i] = (f_X[i] - fi_X_i)^2
  }
  
  list(mean=mean(Int_sqr_err) / var_f_x, sd=sd(Int_sqr_err) / (sqrt(n*var_f_x)))
}
```

## Jiang and Owen (2003) Shrinkage approach. 

```{r SQR}
start_time_SQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")
clusterExport(cl, "wingweight")

clusterSetRNGStream(cl)

QRS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  
  X = gen_unif_mat(n, d)
  f_X = sapply(1:n, FUN=function(j){wingweight(X[j,])})
  
  QRS_output = QRS_true(n, U, X, f_X, true_betas,oracle_shrinkage=FALSE)
  QRS_output
})

stopCluster(cl)

end_time_SQR <- proc.time() - start_time_SQR
```

## Collect important info.

```{r}
betasQRS_Q = matrix(0, nrow=nrow(U), ncol=num_cores)
betaerrQRS_Q = matrix(0, nrow=n, ncol=num_cores)

for (i in 1:num_cores){
  betasQRS_Q[,i] = QRS_PAR_OUT[[i]][[22]]
  betaerrQRS_Q[,i] = QRS_PAR_OUT[[i]][[25]]
}

```

## Compute LOF estimates.

```{r}
LOF_QRS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, wingweight, U, betas = QRS_PAR_OUT[[j]][[3*i-2]], gamma=QRS_PAR_OUT[[j]][[3*i]])$mean
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Shrinkage Sensitivity Analysis For QRS

``` {r SA OQR}
output = sensitivity_analysis_out(n,d,U,num_cores, wing_data, betasQRS_Q, betaerrQRS_Q, LOF_QRS[1,8]$mean,LOF_QRS[2,8]$sd, nrow(U), end_time_SQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/wings_results_QRS.csv")
```

```{r}
True_rate_QRS = lm(log(apply(betaerrQRS_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_QRS = lm(log(unlist(LOF_QRS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## RQMC of Ordinary Quasi-Regression

```{r RQMC QR}
start_time_RQR <- proc.time()
Q <- 15

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")
clusterExport(cl, "wingweight")

clusterSetRNGStream(cl)

RQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){wingweight(X[j,])})
  
  RQR_output = QR_true(n, U, X, f_X, true_betas)
  RQR_output
})

stopCluster(cl)

end_time_RQR <- proc.time() - start_time_RQR
```

## Collect important info.

```{r}
betasRQR_Q = matrix(0, nrow=nrow(U), ncol=num_cores)
betaerrRQR_Q = matrix(0, nrow=n, ncol=num_cores)

for (i in 1:num_cores){
  betasRQR_Q[,i] = RQR_PAR_OUT[[i]][[15]]
  betaerrRQR_Q[,i] = RQR_PAR_OUT[[i]][[17]]
}

```

## Compute LOF estimates.

```{r}
LOF_RQR = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, wingweight, U, betas = RQR_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
output = sensitivity_analysis_out(n,d,U,num_cores, wing_data, betasRQR_Q, betaerrRQR_Q, LOF_RQR[1,8]$mean,LOF_RQR[2,8]$sd, nrow(U), end_time_RQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/wings_results_RQR.csv")
```

```{r}
True_rate_RQR = lm(log(apply(betaerrRQR_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_RQR = lm(log(unlist(LOF_RQR[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```


## MARQRNS

```{r RQMC MARQR}
start_time_MARQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")
clusterExport(cl, "wingweight")

clusterSetRNGStream(cl)

MARQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  f_X <- sapply(1:m, FUN=function(j){wingweight(X[j,])})
  RQR_output = MAQRNS(m,3,8,4,X,f_X,0.00001)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  true_betas_spar = true_betas[sel_basis]
  true_betas_ns = true_betas[!sel_basis]
  true_betas_trun_error = mean(true_betas_ns^2)
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){wingweight(X[j,])})
  
  MARQR_output = QR_true(n, U_spar, X, f_X, true_betas_spar)
  MARQR_output[[length(MARQR_output) + 1]] = U_spar
  MARQR_output[[length(MARQR_output) + 1]] = true_betas_trun_error
  MARQR_output
})

stopCluster(cl)

end_time_MARQR <- proc.time() - start_time_MARQR
```

## Collect important info.

```{r}
betasMARQR_Q = list()
betaerrMARQR_Q = matrix(0, nrow=n, ncol=num_cores)
U_MARQR = list()

for (i in 1:num_cores){
  betasMARQR_Q[[i]] = MARQR_PAR_OUT[[i]][[15]]
  betaerrMARQR_Q[,i] = MARQR_PAR_OUT[[i]][[17]] + MARQR_PAR_OUT[[i]][[19]]
  U_MARQR[[i]] = MARQR_PAR_OUT[[i]][[18]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQR = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, wingweight, U_MARQR[[j]], betas = MARQR_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_ABS_out(n,d,U_MARQR,num_cores, wing_data, betasMARQR_Q, betaerrMARQR_Q, LOF_MARQR[1,8]$mean,LOF_MARQR[2,8]$sd, end_time_MARQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/wings_results_MARQR.csv")
```

```{r}
True_rate_MARQR = lm(log(apply(betaerrMARQR_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_MARQR = lm(log(unlist(LOF_MARQR[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## MARQRSA

```{r RQMC MARQR}
start_time_MARQRSA <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")
clusterExport(cl, "wingweight")

clusterSetRNGStream(cl)

MARQRSA_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  f_X <- sapply(1:m, FUN=function(j){wingweight(X[j,])})
  RQR_output = MAQRSA(m,3,8,4,X,f_X,0.0001)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  true_betas_spar = true_betas[sel_basis]
  true_betas_ns = true_betas[!sel_basis]
  true_betas_trun_error = mean(true_betas_ns^2)
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){wingweight(X[j,])})
  
  MARQRSA_output = QR_true(n, U_spar, X, f_X, true_betas_spar)
  MARQRSA_output[[length(MARQRSA_output) + 1]] = U_spar
  MARQRSA_output[[length(MARQRSA_output) + 1]] = true_betas_trun_error
  MARQRSA_output
})

stopCluster(cl)

end_time_MARQRSA <- proc.time() - start_time_MARQRSA
```

## Collect important info.

```{r}
betasMARQRSA_Q = list()
betaerrMARQRSA_Q = matrix(0, nrow=n, ncol=num_cores)
U_MARQRSA = list()

for (i in 1:num_cores){
  betasMARQRSA_Q[[i]] = MARQRSA_PAR_OUT[[i]][[15]]
  betaerrMARQRSA_Q[,i] = MARQRSA_PAR_OUT[[i]][[17]] + MARQRSA_PAR_OUT[[i]][[19]]
  U_MARQRSA[[i]] = MARQRSA_PAR_OUT[[i]][[18]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQRSA = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, wingweight, U_MARQRSA[[j]], betas = MARQRSA_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
# var_rate_MARQRSA = lm(log(vars_MARQRSA) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_ABS_out(n,d,U_MARQRSA,num_cores, wing_data, betasMARQRSA_Q, betaerrMARQRSA_Q, LOF_MARQRSA[1,8]$mean,LOF_MARQRSA[2,8]$sd, end_time_MARQRSA[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/wings_results_MARQRSA.csv")
```

```{r}
True_rate_MARQRSA = lm(log(apply(betaerrMARQRSA_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_MARQRSA = lm(log(unlist(LOF_MARQRSA[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## MARQRLS

```{r RQMC MARQR}
start_time_MARQRLS <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")
clusterExport(cl, "wingweight")

clusterSetRNGStream(cl)

MARQRLS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  f_X <- sapply(1:m, FUN=function(j){wingweight(X[j,])})
  RQR_output = MAQRLS(m,3,8,4,X,f_X)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  true_betas_spar = true_betas[sel_basis]
  true_betas_ns = true_betas[!sel_basis]
  true_betas_trun_error = mean(true_betas_ns^2)
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){wingweight(X[j,])})
  
  MARQRLS_output = QR_true(n, U_spar, X, f_X, true_betas_spar)
  MARQRLS_output[[length(MARQRLS_output) + 1]] = U_spar
  MARQRLS_output[[length(MARQRLS_output) + 1]] = true_betas_trun_error
  MARQRLS_output
})

stopCluster(cl)

end_time_MARQRLS <- proc.time() - start_time_MARQRLS
```

## Collect important info.

```{r}
betasMARQRLS_Q = list()
betaerrMARQRLS_Q = matrix(0, nrow=n, ncol=num_cores)
U_MARQRLS = list()

for (i in 1:num_cores){
  betasMARQRLS_Q[[i]] = MARQRLS_PAR_OUT[[i]][[15]]
  betaerrMARQRLS_Q[,i] = MARQRLS_PAR_OUT[[i]][[17]] + MARQRLS_PAR_OUT[[i]][[19]]
  U_MARQRLS[[i]] = MARQRLS_PAR_OUT[[i]][[18]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQRLS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, wingweight, U_MARQRLS[[j]], betas = MARQRLS_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
# var_rate_MARQRLS = lm(log(vars_MARQRLS) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_ABS_out(n,d,U_MARQRLS,num_cores, wing_data, betasMARQRLS_Q, betaerrMARQRLS_Q, LOF_MARQRLS[1,8]$mean,LOF_MARQRLS[2,8]$sd, end_time_MARQRLS[[3]])


write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/wings_results_MARQRLS.csv")
```
```{r}
True_rate_MARQRLS = lm(log(apply(betaerrMARQRLS_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_MARQRLS = lm(log(unlist(LOF_MARQRLS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## Results

```{r LOF fits}
plot(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_RQR[1,])), xlab="log(n)", ylab="log(LOF)", ylim=c(-9,5.5), col="blue")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_RQR[1,])), col="blue")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_QRS[1,])),col="green")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_QRS[1,])),col="green")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQR[1,])), col="purple")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQR[1,])), col="purple")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRSA[1,])), col="pink")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRSA[1,])), col="pink")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRLS[1,])), col="black")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRLS[1,])), col="black")
legend(10, 5.5, legend=c(paste0("RQR (", round(LOF_rate_RQR, 4), ")"), paste0("QRS (", round(LOF_rate_QRS, 4), ")"), paste0("MARQRNS (", round(LOF_rate_MARQR, 4), ")"), paste0("MARQRSA (", round(LOF_rate_MARQRSA, 4), ")"),  paste0("MARQRLS (", round(LOF_rate_MARQRLS, 4), ")")),
       col=c("blue", "green", "purple", "pink", "black"), lty=1)
```

```{r Beta Err fits}
# LOF curves
plot(log(1:n), log(apply(betaerrRQR_Q, MARGIN =1, FUN=mean)), xlab="log(n)", ylim=c(-5,30), 
     col="blue", type="l", main="The Average True Beta Difference curves on the log-scale",
     ylab="log(Beta_diff)")
lines(log(1:n), log(apply(betaerrQRS_Q, MARGIN =1, FUN=mean)), col="green")
lines(log(1:n), log(apply(betaerrMARQR_Q, MARGIN =1, FUN=mean)), col="purple")
lines(log(1:n), log(apply(betaerrMARQRSA_Q, MARGIN =1, FUN=mean)), col="pink")
lines(log(1:n), log(apply(betaerrMARQRLS_Q, MARGIN =1, FUN=mean)), col="black")
legend(1, 12, legend=c(paste0("RQR (", round(True_rate_RQR, 4), ")"), paste0("QRS (", round(True_rate_QRS, 4), ")"), paste0("MARQR (", round(True_rate_MARQR, 4), ")"), paste0("MAQRSA (", round(True_rate_MARQRSA, 4), ")"), paste0("MARQRLS (", round(True_rate_MARQRLS, 4), ")")),
       col=c("blue", "green", "purple", "pink", "black"), lty=1)
```


```{r runtime}
end_time_SQR[[3]]
end_time_RQR[[3]]
end_time_MARQR[[3]]
end_time_MARQRSA[[3]]
end_time_MARQRLS[[3]]
```