---
title: "Breast Rcpp"
author: "Ambrose Emmett-Iwaniw"
date: "18/3/2025"
output: pdf_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
library(kernlab)
library(dplyr)
library(caret) # Classification and Regression Training
library(qrng)
library(e1071)
library(Rcpp)
library(parallel)
setwd('C:/Users/arsemmet/Desktop/QR Paper Code')
sourceCpp('QR_code.cpp')
sourceCpp('Adaptive_QR_helper.cpp')
source('sensitivity_analysis.R')
source('data_preparation.R') 
source("scrambled_sobol.R")
set.seed(20669099)
```

# Training the NN Model.

## Data Preparation

```{r}
# Loading data and shows their attribute.
cancer <- read.csv("data.csv")

# exclude columns id and X since they are not attributes of determining cancer  
cancer <- select(cancer, -c(id, X))

# Check if data has any null values in any columns we are searching for.
sum(is.na(cancer))

diagnosis = recode_factor(cancer$diagnosis, 'M' = '1', 'B' = '0')
cancer$diagnosis = diagnosis
```

```{r DP}
# Data Preparation.
diagnosis <- cancer$diagnosis
#diagnosis = as.numeric(diagnosis) - 1
cancer_data <- cancer[,-1]

min_cancer <- as.double(apply(cancer_data,2,min))
max_cancer <- as.double(apply(cancer_data,2,max))

cancer_data = sweep(cancer_data, 2, min_cancer)
cancer_data = sweep(cancer_data, 2, max_cancer - min_cancer, FUN='/')

cancer_data = cbind(cancer_data, diagnosis)

n <- 2^16
m <- 2^16
d <- ncol(cancer_data) - 1
```

```{r DP}
B0 = 3
B1 = 6
Binf = 3
# Finite interpretable sets (Arbitrary)
U <- interpretable_poly_sets(d, B0,B1,Binf) # 3,8,4
U = do.call(rbind, U)
nrow(U)
```

## Splitting Data
```{r}
#set random seed number to get reproducible model
set.seed(13)

# Building subsets
TrainingIndex <- createDataPartition(cancer_data$diagnosis, p = 0.8, list = FALSE)
trainingSet <- cancer[TrainingIndex,] #80% random data points
testingSet <- cancer[-TrainingIndex,] #the rest 20%

#Check if the TrainingIndex is randomly chosen
head(TrainingIndex, 10) # looks good
```

# Training model

```{r}
# NN black-box optimized.
library(nnet)
bestmod = nnet(diagnosis ~ ., data=trainingSet, size=10, decay=1e-4, rang=0.1, abstol=1e-10, maxit=1500)

# training accuarcy
print(mean(predict(bestmod,trainingSet, type = "class") == trainingSet$diagnosis))
print(mean(predict(bestmod, testingSet, type="class") == testingSet$diagnosis))

#summary(bestmod)
```

```{r}
W_h = t(matrix(bestmod$wts[1:310], byrow=TRUE, ncol=10))
#sigmoid(x)
W_o = bestmod$wts[311:321]

f_nn <- function(x){
  x <- c(1,x)
  outp = sum(c(1,sigmoid(W_h %*% x)) * W_o)
  outp
}

f_nn_vector <- function(X){
  f_out = vector(length=nrow(X))
  
  for (i in 1:nrow(X)){
    f_out[i] = f_nn(X[i,])
  }
  
  f_out
}

#f_X = f_nn_vector(gen_unif_mat(n, d))
```

```{r}
plot(predict(bestmod, testingSet))
lines(sort(predict(bestmod, testingSet)))
```

## Code to compute LOF.

```{r}
LOF_EST <- function(d, U, betas, gamma=vector(), n=5000){
  Int_sqr_err = rep(NA, n)
  
  if (length(gamma) == 0)
    gamma = rep(1, nrow(U))
  
  X = gen_unif_mat(n, d)
  f_X = f_nn_vector(X)
  var_f_x = var(f_X)
  
  Int_sqr_err = LOF_EST_cpp(d, X, f_X, var_f_x, U, betas, gamma, n=n)
  
  list(mean=mean(Int_sqr_err) / var_f_x, sd=sd(Int_sqr_err) / (sqrt(n*var_f_x)), ISE_mean=mean(Int_sqr_err),  ISE_sd=sd(Int_sqr_err) / sqrt(n))
}
```

## Jiang and Owen (2003) Shrinkage approach. 

```{r SQR}
start_time_SQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "W_h")
clusterExport(cl, "W_o")
clusterExport(cl, "f_nn")
clusterExport(cl, "f_nn_vector")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

QRS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(e1071)
  sourceCpp('QR_code.cpp')
  
  X = gen_unif_mat(n, d)
  f_X = f_nn_vector(X)
  
  QRS_output = QRS_email(n, U, X, f_X,oracle_shrinkage=FALSE)
  
   # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U, betas = QRS_output[[3*i-2]], gamma=QRS_output[[3*i]])$mean
  })
  
  QRS_output[[length(QRS_output) + 1]] = LOF_val
  QRS_output
})

stopCluster(cl)

end_time_SQR <- proc.time() - start_time_SQR
```

## Collect important info.

```{r}
betasQRS_Q = matrix(0, nrow=nrow(U), ncol=num_cores)
LOF_QRS = list()
para_indx = n_steps * 3 - 2

for (i in 1:num_cores){
  betasQRS_Q[,i] = QRS_PAR_OUT[[i]][[para_indx]]
  LOF_QRS[[i]] = QRS_PAR_OUT[[i]][[3*n_steps+1]]
}

LOF_QRS = do.call(rbind, LOF_QRS)

```

## Shrinkage Sensitivity Analysis For QRS

``` {r SA OQR}
LOF_QRS_mean = mean(LOF_QRS[,n_steps]) 
LOF_QRS_sd = sd(LOF_QRS[,n_steps]) / sqrt(num_cores)
output = sensitivity_analysis_QR_ABS(n,d,U,num_cores, cancer_data, betasQRS_Q, LOF_QRS_mean,LOF_QRS_sd, end_time_SQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Breast_results_QRS.csv")
```

```{r}
LOF_rate_QRS = lm(log(LOF_QRS[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## RQMC of Ordinary Quasi-Regression

```{r RQR}
start_time_RQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "W_h")
clusterExport(cl, "W_o")
clusterExport(cl, "f_nn")
clusterExport(cl, "f_nn_vector")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

RQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(kernlab)
  library(e1071)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  source("scrambled_sobol.R")
  
  #X = sobol(n, d, randomize = "digital.shift")
  X = scrambled_sobol(log2(n), d, seed=sample.int(100000))
  f_X = f_nn_vector(X)
  
  RQR_output = QR_email(n, U, X, f_X)
  
  # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U, betas = RQR_output[[2*i-1]])$mean
  })
  
  RQR_output[[length(RQR_output) + 1]] = LOF_val
  RQR_output
})

stopCluster(cl)

end_time_RQR <- proc.time() - start_time_RQR
```

## Collect important info.

```{r}
betasRQR_Q = matrix(0, nrow=nrow(U), ncol=num_cores)
LOF_RQR = list()
para_indx = n_steps * 2 - 1

for (i in 1:num_cores){
  betasRQR_Q[,i] = RQR_PAR_OUT[[i]][[para_indx]]
  LOF_RQR[[i]] = RQR_PAR_OUT[[i]][[2*n_steps+1]]
}

LOF_RQR = do.call(rbind, LOF_RQR)
```

## Shrinkage Sensitivity Analysis For RQR

``` {r SA OQR}
LOF_RQR_mean = mean(LOF_RQR[,n_steps]) 
LOF_RQR_sd = sd(LOF_RQR[,n_steps]) / sqrt(num_cores)
output = sensitivity_analysis_QR_ABS(n,d,U,num_cores, cancer_data, betasRQR_Q, LOF_RQR_mean,LOF_RQR_sd, end_time_RQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Breast_results_RQR.csv")
```

```{r}
LOF_rate_RQR = lm(log(LOF_RQR[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## MARQRNS

```{r RQMC MARQR}
start_time_MARQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "B0")
clusterExport(cl, "B1")
clusterExport(cl, "Binf")
clusterExport(cl, "W_h")
clusterExport(cl, "W_o")
clusterExport(cl, "f_nn")
clusterExport(cl, "f_nn_vector")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

MARQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(kernlab)
  library(e1071)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  source("scrambled_sobol.R")
  
  #X = sobol(m, d, randomize = "digital.shift")
  X = scrambled_sobol(log2(m), d, seed=sample.int(100000))
  f_X = f_nn_vector(X)
  
  RQR_output = MAQRNS(m,B0,B1,Binf,X,f_X,1e-15)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  #X = sobol(n, d, randomize = "digital.shift")
  X = scrambled_sobol(log2(n), d, seed=sample.int(100000))
  f_X = f_nn_vector(X)
  
  MARQR_output = QR_adap(n, U_spar, X, f_X)
  MARQR_output[[length(MARQR_output) + 1]] = U_spar
  
  # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U_spar, betas = MARQR_output[[2*i-1]])$mean
  })
  
  MARQR_output[[length(MARQR_output) + 1]] = LOF_val
  
  MARQR_output
})

stopCluster(cl)

end_time_MARQR <- proc.time() - start_time_MARQR
```

## Collect important info.

```{r}
betasMARQR_Q = list()
U_MARQR = list()
LOF_MARQR = list()

for (i in 1:num_cores){
  betasMARQR_Q[[i]] = MARQR_PAR_OUT[[i]][[2*n_steps - 1]]
  U_MARQR[[i]] = MARQR_PAR_OUT[[i]][[2*n_steps+1]]
  LOF_MARQR[[i]] = MARQR_PAR_OUT[[i]][[2*n_steps+2]]
}

LOF_MARQR = do.call(rbind, LOF_MARQR)

```

## Senstivity Analysis For RQR

``` {r SA OQR}
LOF_MARQR_mean = mean(LOF_MARQR[,n_steps]) 
LOF_MARQR_sd = sd(LOF_MARQR[,n_steps]) / sqrt(num_cores)
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQR,num_cores, cancer_data, betasMARQR_Q, LOF_MARQR_mean,LOF_MARQR_sd, end_time_MARQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Breast_results_MARQR.csv")
```

```{r}
LOF_rate_MARQR = lm(log(LOF_MARQR[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## MARQRSA

```{r RQMC MARQRSA}
start_time_MARQRSA <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "B0")
clusterExport(cl, "B1")
clusterExport(cl, "Binf")
clusterExport(cl, "W_h")
clusterExport(cl, "W_o")
clusterExport(cl, "f_nn")
clusterExport(cl, "f_nn_vector")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

MARQRSA_PAR_OUT = clusterEvalQ(cl, 
             {
  library(kernlab)
  library(e1071)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  source("scrambled_sobol.R")
  
  #X = sobol(m, d, randomize = "digital.shift")
  X = scrambled_sobol(log2(m), d, seed=sample.int(100000))
  f_X = f_nn_vector(X)
  
  RQR_output = MAQRSA(m,B0,B1,Binf,X,f_X,0.001)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  #X = sobol(n, d, randomize = "digital.shift")
  X = scrambled_sobol(log2(n), d, seed=sample.int(100000))
  f_X = f_nn_vector(X)
  
  MARQRSA_output = QR_adap(n, U_spar, X, f_X)
  MARQRSA_output[[length(MARQRSA_output) + 1]] = U_spar
  
  # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U_spar, betas = MARQRSA_output[[2*i-1]])$mean
  })
  
  MARQRSA_output[[length(MARQRSA_output) + 1]] = LOF_val
  MARQRSA_output
})

stopCluster(cl)

end_time_MARQRSA <- proc.time() - start_time_MARQRSA
```

## Collect important info.

```{r}
betasMARQRSA_Q = list()
U_MARQRSA = list()
LOF_MARQRSA = list()

for (i in 1:num_cores){
  betasMARQRSA_Q[[i]] = MARQRSA_PAR_OUT[[i]][[2*n_steps - 1]]
  U_MARQRSA[[i]] = MARQRSA_PAR_OUT[[i]][[2*n_steps+1]]
  LOF_MARQRSA[[i]] = MARQRSA_PAR_OUT[[i]][[2*n_steps+2]]
}

LOF_MARQRSA = do.call(rbind, LOF_MARQRSA)

```

## Senstivity Analysis For RQR

``` {r SA OQR}
LOF_MARQRSA_mean = mean(LOF_MARQRSA[,n_steps]) 
LOF_MARQRSA_sd = sd(LOF_MARQRSA[,n_steps]) / sqrt(num_cores)
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQRSA,num_cores, cancer_data, betasMARQRSA_Q, LOF_MARQRSA_mean,LOF_MARQRSA_sd, end_time_MARQRSA[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Breast_results_MARQRSA.csv")
```

```{r}
LOF_rate_MARQRSA = lm(log(LOF_MARQRSA[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## MARQROS

```{r RQMC MARQROS}
start_time_MARQROS <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "B0")
clusterExport(cl, "B1")
clusterExport(cl, "Binf")
clusterExport(cl, "W_h")
clusterExport(cl, "W_o")
clusterExport(cl, "f_nn")
clusterExport(cl, "f_nn_vector")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

MARQROS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(kernlab)
  library(e1071)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  source("scrambled_sobol.R")
  
  #X = sobol(m, d, randomize = "digital.shift")
  X = scrambled_sobol(log2(m), d, seed=sample.int(100000))
  f_X = f_nn_vector(X)
  
  RQR_output = MAQROS(m,B0,B1,Binf,X,f_X)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  #X = sobol(n, d, randomize = "digital.shift")
  X = scrambled_sobol(log2(n), d, seed=sample.int(100000))
  f_X = f_nn_vector(X)
  
  MARQROS_output = QR_adap(n, U_spar, X, f_X)
  MARQROS_output[[length(MARQROS_output) + 1]] = U_spar
  
  # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U_spar, betas = MARQROS_output[[2*i-1]])$mean
  })
  
  MARQROS_output[[length(MARQROS_output) + 1]] = LOF_val
  MARQROS_output
})

stopCluster(cl)

end_time_MARQROS <- proc.time() - start_time_MARQROS
```

## Collect important info.

```{r}
betasMARQROS_Q = list()
U_MARQROS = list()
LOF_MARQROS = list()

for (i in 1:num_cores){
  betasMARQROS_Q[[i]] = MARQROS_PAR_OUT[[i]][[2*n_steps - 1]]
  U_MARQROS[[i]] = MARQROS_PAR_OUT[[i]][[2*n_steps+1]]
  LOF_MARQROS[[i]] = MARQROS_PAR_OUT[[i]][[2*n_steps+2]]
}

LOF_MARQROS = do.call(rbind, LOF_MARQROS)

```

## Senstivity Analysis For RQR

``` {r SA OQR}
LOF_MARQROS_mean = mean(LOF_MARQROS[,n_steps]) 
LOF_MARQROS_sd = sd(LOF_MARQROS[,n_steps]) / sqrt(num_cores)
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQROS,num_cores, cancer_data, betasMARQROS_Q, LOF_MARQROS_mean, LOF_MARQROS_sd, end_time_MARQROS[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Breast_results_MARQROS.csv")
```

```{r}
LOF_rate_MARQROS = lm(log(LOF_MARQROS[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## Results

```{r LOF fits}
LOF_x_axis = log(2^seq(10,log2(n),1))
plot(LOF_x_axis, log(LOF_RQR[1,]), xlab="log(n)", ylab="LOF", ylim=c(-5.5,5.5), col="blue")
lines(LOF_x_axis, log(LOF_RQR[1,]), col="blue")
points(LOF_x_axis, log(LOF_QRS[1,]),col="green")
lines(LOF_x_axis, log(LOF_QRS[1,]),col="green")
points(LOF_x_axis, log(LOF_MARQR[1,]), col="purple")
lines(LOF_x_axis, log(LOF_MARQR[1,]), col="purple")
points(LOF_x_axis, log(LOF_MARQRSA[1,]), col="pink")
lines(LOF_x_axis, log(LOF_MARQRSA[1,]), col="pink")
points(LOF_x_axis, log(LOF_MARQROS[1,]), col="black")
lines(LOF_x_axis, log(LOF_MARQROS[1,]), col="black")
legend(10, 5.5, legend=c(paste0("RQR (", round(LOF_rate_RQR, 4), ")"), paste0("QRS (", round(LOF_rate_QRS, 4), ")"), paste0("MARQR (", round(LOF_rate_MARQR, 4), ")"), paste0("MARQRSA (", round(LOF_rate_MARQRSA, 4), ")"),  paste0("MARQROS (", round(LOF_rate_MARQROS, 4), ")")),
       col=c("blue", "green", "purple", "pink", "black"), lty=1)
```


```{r runtime}
end_time_SQR[[3]]
end_time_RQR[[3]]
end_time_MARQR[[3]]
end_time_MARQRSA[[3]]
end_time_MARQROS[[3]]
```