---
title: "Art Sparse Rcpp"
author: "Ambrose Emmett-Iwaniw"
date: "16/8/2023"
output: pdf_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
library(MASS)
library(qrng)
library(Rcpp)
library(parallel)
sourceCpp('C:/Users/ambro/Desktop/AQR Paper Code/QR_code.cpp')
sourceCpp('C:/Users/ambro/Desktop/AQR Paper Code/Adaptive_QR_helper.cpp')
source('C:/Users/ambro/Desktop/AQR Paper Code/sensitivity_analysis.R')
source('C:/Users/ambro/Desktop/AQR Paper Code/data_preparation.R')
set.seed(20669099)
```

## Data Preparation
```{r DP}
artifical_sparse_data <- data.frame(matrix(ncol = 8, nrow = 0))
colnames(artifical_sparse_data) <- c("x1", "x2", "x3", "x4", "x5", "x6", "x7", "x8")
n <- 2^17
m <- 2^15
d <- 8
# Finite interpretable sets (Arbitrary)
U <- interpretable_sets(d,3,4,3)
U = do.call(rbind, U)
```

# True Beta coefficients.

```{r}
true_betas = sapply(1:nrow(U), FUN=function(j){
  if (sum(U[j,] > 0) <= 2 && sum(U[j,]) <= 2 && max(U[j,]) <= 2)
    (0.8)^sum(U[j,])
  else
    0
})
```

# Why is Art. Dense function is Dense?

```{r}
nrow(U)
total_betas = sum(true_betas[-1]^2)
sum(sort(true_betas[-1]^2, decreasing = TRUE)[1:20]) / total_betas
sum(sort(true_betas[-1]^2, decreasing = TRUE)[1:30]) / total_betas
sum(sort(true_betas[-1]^2, decreasing = TRUE)[1:40]) / total_betas
```

## Code to compute LOF.

```{r}
LOF_EST <- function(d, betas, gamma=vector(), true_betas_r){
  if (length(gamma) == 0)
    gamma = rep(1, nrow(U))
  
  sum((gamma*betas - true_betas_r)^2) / sum(true_betas_r[-1]^2)
}

LOF_EST_MA <- function(betas, true_betas_r, total_var){
  sum((betas - true_betas_r)^2) / total_var
}
```


## Jiang and Owen (2003) Shrinkage approach. 

```{r SQR}
start_time_SQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")

clusterSetRNGStream(cl)

QRS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  
  X = gen_unif_mat(n, d)
  f_X = sapply(1:n, FUN=function(j){artifical_sparse_function(U, X[j,])})
  
  QRS_output = QRS_true(n, U, X, f_X, true_betas, oracle_shrinkage = FALSE)
  QRS_output
})

stopCluster(cl)

end_time_SQR <- proc.time() - start_time_SQR
```

## Collect important info.

```{r}
betasQRS_Q = matrix(0, nrow=nrow(U), ncol=num_cores)
betaerrQRS_Q = matrix(0, nrow=n, ncol=num_cores)

for (i in 1:num_cores){
  betasQRS_Q[,i] = QRS_PAR_OUT[[i]][[22]]
  betaerrQRS_Q[,i] = QRS_PAR_OUT[[i]][[25]]
}

```

## Collect important info.

```{r}
betasQRS_Q = matrix(0, nrow=nrow(U), ncol=num_cores)
betaerrQRS_Q = matrix(0, nrow=n, ncol=num_cores)

for (i in 1:num_cores){
  betasQRS_Q[,i] = QRS_PAR_OUT[[i]][[22]]
  betaerrQRS_Q[,i] = QRS_PAR_OUT[[i]][[25]]
}

```

## Compute LOF estimates.

```{r}
LOF_QRS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, betas = QRS_PAR_OUT[[j]][[3*i-2]], gamma=QRS_PAR_OUT[[j]][[3*i]], true_betas_r = true_betas)
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est)/ sqrt(num_cores))})
```

## Shrinkage Sensitivity Analysis For QRS

``` {r SA OQR}
output = sensitivity_analysis_out(n,d,U,num_cores, artifical_sparse_data, betasQRS_Q, betaerrQRS_Q, LOF_QRS[1,8]$mean,LOF_QRS[2,8]$sd, nrow(U), end_time_SQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/art_sparse_results_QRS.csv")
```

```{r}
True_rate_QRS = lm(log(apply(betaerrQRS_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_QRS = lm(log(unlist(LOF_QRS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## RQMC of Ordinary Quasi-Regression

```{r RQMC QR}
start_time_RQR <- proc.time()
Q <- 15

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")

clusterSetRNGStream(cl)

RQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){artifical_sparse_function(U,X[j,])})
  
  RQR_output = QR_true(n, U, X, f_X, true_betas)
  RQR_output
})

stopCluster(cl)

end_time_RQR <- proc.time() - start_time_RQR
```

## Collect important info.

```{r}
betasRQR_Q = matrix(0, nrow=nrow(U), ncol=num_cores)
betaerrRQR_Q = matrix(0, nrow=n, ncol=num_cores)

for (i in 1:num_cores){
  betasRQR_Q[,i] = RQR_PAR_OUT[[i]][[15]]
  betaerrRQR_Q[,i] = RQR_PAR_OUT[[i]][[17]]
}

```

## Compute LOF estimates.

```{r}
LOF_RQR = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, betas = RQR_PAR_OUT[[j]][[2*i-1]], true_betas_r = true_betas)
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est)/ sqrt(num_cores))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
output = sensitivity_analysis_out(n,d,U,num_cores, artifical_sparse_data, betasRQR_Q, betaerrRQR_Q, LOF_RQR[1,8]$mean,LOF_RQR[2,8]$sd, nrow(U), end_time_RQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/art_sparse_results_RQR.csv")
```

```{r}
True_rate_RQR = lm(log(apply(betaerrRQR_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_RQR = lm(log(unlist(LOF_RQR[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## MARQRSA

```{r RQMC MARQR}
start_time_MARQRSA <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")

clusterSetRNGStream(cl)

MARQRSA_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  f_X <- sapply(1:m, FUN=function(j){artifical_sparse_function(U,X[j,])})
  RQR_output = MAQRSA(m,3,4,3,X,f_X,0.02)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  true_betas_spar = true_betas[sel_basis]
  true_betas_ns = true_betas[!sel_basis]
  true_betas_trun_error = mean(true_betas_ns^2)
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){artifical_sparse_function(U,X[j,])})
  
  MARQRSA_output = QR_true(n, U_spar, X, f_X, true_betas_spar)
  MARQRSA_output[[length(MARQRSA_output) + 1]] = U_spar
  MARQRSA_output[[length(MARQRSA_output) + 1]] = true_betas_trun_error
   MARQRSA_output[[length(MARQRSA_output) + 1]] = true_betas_spar
  MARQRSA_output
})

stopCluster(cl)

end_time_MARQRSA <- proc.time() - start_time_MARQRSA
```

## Collect important info.

```{r}
betasMARQRSA_Q = list()
betaerrMARQRSA_Q = matrix(0, nrow=n, ncol=num_cores)
U_MARQRSA = list()

for (i in 1:num_cores){
  betasMARQRSA_Q[[i]] = MARQRSA_PAR_OUT[[i]][[15]]
  betaerrMARQRSA_Q[,i] = MARQRSA_PAR_OUT[[i]][[17]] + MARQRSA_PAR_OUT[[i]][[19]]
  U_MARQRSA[[i]] = MARQRSA_PAR_OUT[[i]][[18]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQRSA = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST_MA(betas = MARQRSA_PAR_OUT[[j]][[2*i-1]], true_betas_r = MARQRSA_PAR_OUT[[j]][[20]], total_var = sum(true_betas[-1]^2)) + MARQRSA_PAR_OUT[[j]][[19]] / sum(true_betas[-1]^2)
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
# var_rate_MARQRSA = lm(log(vars_MARQRSA) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_ABS_out(n,d,U_MARQRSA,num_cores, artifical_sparse_data, betasMARQRSA_Q, betaerrMARQRSA_Q, LOF_MARQRSA[1,8]$mean,LOF_MARQRSA[2,8]$sd, end_time_MARQRSA[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/art_sparse_results_MARQRSA.csv")
```
```{r}
True_rate_MARQRSA = lm(log(apply(betaerrMARQRSA_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_MARQRSA = lm(log(unlist(LOF_MARQRSA[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## MARQROS

```{r RQMC MARQR}
start_time_MARQROS <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")

clusterSetRNGStream(cl)

MARQROS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Paper Code/QR_code.cpp')
  sourceCpp('C:/Users/arsemmet/Desktop/QR Paper Code/Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  f_X <- sapply(1:m, FUN=function(j){artifical_sparse_function(U,X[j,])})
  RQR_output = MAQROS(m,3,4,3,X,f_X)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  true_betas_spar = true_betas[sel_basis]
  true_betas_ns = true_betas[!sel_basis]
  true_betas_trun_error = mean(true_betas_ns^2)
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){artifical_sparse_function(U,X[j,])})
  
  MARQROS_output = QR_true(n, U_spar, X, f_X, true_betas_spar)
  MARQROS_output[[length(MARQROS_output) + 1]] = U_spar
  MARQROS_output[[length(MARQROS_output) + 1]] = true_betas_trun_error
  MARQROS_output[[length(MARQROS_output) + 1]] = true_betas_spar
  MARQROS_output
})

stopCluster(cl)

end_time_MARQROS <- proc.time() - start_time_MARQROS
```

## Collect important info.

```{r}
betasMARQROS_Q = list()
betaerrMARQROS_Q = matrix(0, nrow=n, ncol=num_cores)
U_MARQROS = list()

for (i in 1:num_cores){
  betasMARQROS_Q[[i]] = MARQROS_PAR_OUT[[i]][[15]]
  betaerrMARQROS_Q[,i] = MARQROS_PAR_OUT[[i]][[17]] + MARQROS_PAR_OUT[[i]][[19]]
  U_MARQROS[[i]] = MARQROS_PAR_OUT[[i]][[18]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQROS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST_MA(betas = MARQROS_PAR_OUT[[j]][[2*i-1]], true_betas_r = MARQROS_PAR_OUT[[j]][[20]], total_var = sum(true_betas[-1]^2)) + MARQROS_PAR_OUT[[j]][[19]] / sum(true_betas[-1]^2)
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Senstivity Analysis For MARQROS

``` {r SA OQR}
# var_rate_MARQROS = lm(log(vars_MARQROS) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_ABS_out(n,d,U_MARQROS,num_cores, artifical_sparse_data, betasMARQROS_Q, betaerrMARQROS_Q, LOF_MARQROS[1,8]$mean,LOF_MARQROS[2,8]$sd, end_time_MARQROS[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/art_sparse_results_MARQROS.csv")
```
```{r}
True_rate_MARQROS = lm(log(apply(betaerrMARQROS_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_MARQROS = lm(log(unlist(LOF_MARQROS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

```{r}
betas_var_true = rep(0,num_cores)

for (i in 1:20){
  betas_var_true[i] = betasMARQROS_Q[[i]][1]
}

var(betas_var_true)
```

## MARQRNNS

```{r RQMC MARQRNNS}
start_time_MARQRNNS <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")

clusterSetRNGStream(cl)

MARQRNNS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Paper Code/QR_code.cpp')
  sourceCpp('C:/Users/arsemmet/Desktop/QR Paper Code/Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  f_X <- sapply(1:m, FUN=function(j){artifical_sparse_function(U,X[j,])})
  RQR_output = MAQRNNS(m,3,4,3,X,f_X,0.05)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  true_betas_spar = true_betas[sel_basis]
  true_betas_ns = true_betas[!sel_basis]
  true_betas_trun_error = mean(true_betas_ns^2)
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){artifical_sparse_function(U,X[j,])})
  
  MARQRNNS_output = QR_true(n, U_spar, X, f_X, true_betas_spar)
  MARQRNNS_output[[length(MARQRNNS_output) + 1]] = U_spar
  MARQRNNS_output[[length(MARQRNNS_output) + 1]] = true_betas_trun_error
  MARQRNNS_output[[length(MARQRNNS_output) + 1]] = true_betas_spar
  MARQRNNS_output
})

stopCluster(cl)

end_time_MARQRNNS <- proc.time() - start_time_MARQRNNS
```

## Collect important info.

```{r}
betasMARQRNNS_Q = list()
betaerrMARQRNNS_Q = matrix(0, nrow=n, ncol=num_cores)
U_MARQRNNS = list()

for (i in 1:num_cores){
  betasMARQRNNS_Q[[i]] = MARQRNNS_PAR_OUT[[i]][[15]]
  betaerrMARQRNNS_Q[,i] = MARQRNNS_PAR_OUT[[i]][[17]] + MARQRNNS_PAR_OUT[[i]][[19]]
  U_MARQRNNS[[i]] = MARQRNNS_PAR_OUT[[i]][[18]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQRNNS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST_MA(betas = MARQRNNS_PAR_OUT[[j]][[2*i-1]], true_betas_r = MARQRNNS_PAR_OUT[[j]][[20]], total_var=sum(true_betas[-1]^2)) + MARQRNNS_PAR_OUT[[j]][[19]] / sum(true_betas[-1]^2)
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
#var_rate_MARQRNNS = lm(log(vars_MARQRNNS) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_ABS_out(n,d,U_MARQRNNS,num_cores, artifical_sparse_data, betasMARQRNNS_Q, betaerrMARQRNNS_Q, LOF_MARQRNNS[1,8]$mean,LOF_MARQRNNS[2,8]$sd, end_time_MARQRNNS[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/art_sparse_results_MARQRNNS.csv")
```
```{r}
True_rate_MARQRNNS = lm(log(apply(betaerrMARQRNNS_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_MARQRNNS = lm(log(unlist(LOF_MARQRNNS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## Results

```{r LOF fits}
plot(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_RQR[1,])), xlab="log(n)", ylab="log(LOF)", ylim=c(-15,2), col="blue")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_RQR[1,])), col="blue")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_QRS[1,])),col="red")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_QRS[1,])),col="red")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRNNS[1,])), col="purple")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRNNS[1,])), lwd=4, col="purple")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRSA[1,])), col="green")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRSA[1,])), lwd=2, col="green")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQROS[1,])), col="black")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQROS[1,])), lwd=1, col="black")
legend(10, 2, legend=c(paste0("RQR (", round(LOF_rate_RQR, 4), ")"), paste0("QRS (", round(LOF_rate_QRS, 4), ")"), paste0("MARQRNNS (", round(LOF_rate_MARQRNNS, 4), ")"), paste0("MARQRSA (", round(LOF_rate_MARQRSA, 4), ")"), paste0("MARQROS (", round(LOF_rate_MARQROS, 4), ")")),
       col=c("blue", "red", "purple", "green", "black"), lty=1)
```

```{r Beta Err fits}
# LOF curves
plot(log(1:n), log(apply(betaerrRQR_Q, MARGIN =1, FUN=mean)), xlab="log(n)", ylim=c(-20,10), 
     col="blue", type="l", main="The Average True Beta Difference curves on the log-scale",
     ylab="log(Beta_diff)")
lines(log(1:n), log(apply(betaerrQRS_Q, MARGIN =1, FUN=mean)), col="red")
lines(log(1:n), log(apply(betaerrMARQRNNS_Q, MARGIN =1, FUN=mean)),lwd=4, col="purple")
lines(log(1:n), log(apply(betaerrMARQRSA_Q, MARGIN =1, FUN=mean)), lwd=2, col="green")
lines(log(1:n), log(apply(betaerrMARQROS_Q, MARGIN =1, FUN=mean)), lwd=1, col="black")
legend(1, -5, legend=c(paste0("RQR (", round(True_rate_RQR, 4), ")"), paste0("QRS (", round(True_rate_QRS, 4), ")"), paste0("MARQRNNS (", round(True_rate_MARQRNNS, 4), ")"), paste0("MAQRSA (", round(True_rate_MARQRSA, 4), ")"), paste0("MARQROS (", round(True_rate_MARQROS, 4), ")")),
       col=c("blue", "red", "purple", "green", "black"), lty=1)
```

```{r runtime}
end_time_SQR[[3]]
end_time_RQR[[3]]
end_time_MARQRNNS[[3]]
end_time_MARQRSA[[3]]
end_time_MARQROS[[3]]
```

# Code not used anymore.

## MARQRNS

```{r RQMC MARQR}
start_time_MARQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")

clusterSetRNGStream(cl)

MARQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  f_X <- sapply(1:m, FUN=function(j){artifical_sparse_function(U,X[j,])})
  RQR_output = MAQRNS(m,3,4,3,X,f_X,0.000001)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  true_betas_spar = true_betas[sel_basis]
  true_betas_ns = true_betas[!sel_basis]
  true_betas_trun_error = mean(true_betas_ns^2)
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){artifical_sparse_function(U,X[j,])})
  
  MARQR_output = QR_true(n, U_spar, X, f_X, true_betas_spar)
  MARQR_output[[length(MARQR_output) + 1]] = U_spar
  MARQR_output[[length(MARQR_output) + 1]] = true_betas_trun_error
  MARQR_output[[length(MARQR_output) + 1]] = true_betas_spar
  MARQR_output
})

stopCluster(cl)

end_time_MARQR <- proc.time() - start_time_MARQR
```

## Collect important info.

```{r}
betasMARQR_Q = list()
betaerrMARQR_Q = matrix(0, nrow=n, ncol=num_cores)
U_MARQR = list()

for (i in 1:num_cores){
  betasMARQR_Q[[i]] = MARQR_PAR_OUT[[i]][[15]]
  betaerrMARQR_Q[,i] = MARQR_PAR_OUT[[i]][[17]] + MARQR_PAR_OUT[[i]][[19]]
  U_MARQR[[i]] = MARQR_PAR_OUT[[i]][[18]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQR = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST_MA(betas = MARQR_PAR_OUT[[j]][[2*i-1]], true_betas_r = MARQR_PAR_OUT[[j]][[20]], total_var=sum(true_betas[-1]^2)) + MARQR_PAR_OUT[[j]][[19]] / sum(true_betas[-1]^2)
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_ABS_out(n,d,U_MARQR,num_cores, artifical_sparse_data, betasMARQR_Q, betaerrMARQR_Q, LOF_MARQR[1,8]$mean,LOF_MARQR[2,8]$sd, end_time_MARQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/art_sparse_results_MARQR.csv")
```

```{r}
True_rate_MARQR = lm(log(apply(betaerrMARQR_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_MARQR = lm(log(unlist(LOF_MARQR[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## MARQRLS

```{r RQMC MARQR}
start_time_MARQRLS <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "true_betas")

clusterSetRNGStream(cl)

MARQRLS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/QR_code.cpp')
  sourceCpp('C:/Users/arsemmet/Desktop/QR Research/Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  f_X <- sapply(1:m, FUN=function(j){artifical_sparse_function(U,X[j,])})
  RQR_output = MAQRLS(m,3,4,3,X,f_X)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  true_betas_spar = true_betas[sel_basis]
  true_betas_ns = true_betas[!sel_basis]
  true_betas_trun_error = mean(true_betas_ns^2)
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  f_X = sapply(1:n, FUN=function(j){artifical_sparse_function(U,X[j,])})
  
  MARQRLS_output = QR_true(n, U_spar, X, f_X, true_betas_spar)
  MARQRLS_output[[length(MARQRLS_output) + 1]] = U_spar
  MARQRLS_output[[length(MARQRLS_output) + 1]] = true_betas_trun_error
  MARQRLS_output[[length(MARQRLS_output) + 1]] = true_betas_spar
  MARQRLS_output
})

stopCluster(cl)

end_time_MARQRLS <- proc.time() - start_time_MARQRLS
```

## Collect important info.

```{r}
betasMARQRLS_Q = list()
betaerrMARQRLS_Q = matrix(0, nrow=n, ncol=num_cores)
U_MARQRLS = list()

for (i in 1:num_cores){
  betasMARQRLS_Q[[i]] = MARQRLS_PAR_OUT[[i]][[15]]
  betaerrMARQRLS_Q[,i] = MARQRLS_PAR_OUT[[i]][[17]] + MARQRLS_PAR_OUT[[i]][[19]]
  U_MARQRLS[[i]] = MARQRLS_PAR_OUT[[i]][[18]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQRLS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST_MA(betas = MARQRLS_PAR_OUT[[j]][[2*i-1]], true_betas_r = MARQRLS_PAR_OUT[[j]][[20]], total_var = sum(true_betas[-1]^2)) + MARQRLS_PAR_OUT[[j]][[19]] / sum(true_betas[-1]^2)
    })
  list(mean=mean(LOF_est), sd=sd(LOF_est) / sqrt(num_cores))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
# var_rate_MARQRLS = lm(log(vars_MARQRLS) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_ABS_out(n,d,U_MARQRLS,num_cores, artifical_sparse_data, betasMARQRLS_Q, betaerrMARQRLS_Q, LOF_MARQRLS[1,8]$mean,LOF_MARQRLS[2,8]$sd, end_time_MARQRLS[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Research/ABS/art_sparse_results_MARQRLS.csv")
```

```{r}
True_rate_MARQRLS = lm(log(apply(betaerrMARQRLS_Q, MARGIN=1, mean)) ~ log(1:n))$coefficients[[2]]
LOF_rate_MARQRLS = lm(log(unlist(LOF_MARQRLS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```