---
title: "CPU Rcpp"
author: "Ambrose Emmett-Iwaniw"
date: "16/8/2023"
output: pdf_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
library(nnet)
library(qrng)
library(Rcpp)
library(caret)
library(MASS)
library(parallel)
setwd('C:/Users/arsemmet/Desktop/QR Paper Code')
sourceCpp('QR_code.cpp')
sourceCpp('Adaptive_QR_helper.cpp')
source('sensitivity_analysis.R')
source('data_preparation.R') 
#source("C:/Users/ambro/Desktop/QR Paper Code/scrambled_sobol.R")
set.seed(20669099)
```

## Data Preparation
```{r DP}
# Data Preparation.
cpu_data <- cpus

# Replace the perf variable.
perf = log(cpu_data$perf, 10)

cpu_data <- cpu_data[,-c(1,8,9)]

# First 3 log transformed.
cpu_data$syct = log(cpu_data$syct,10)
cpu_data$mmin = log(cpu_data$mmin,10)
cpu_data$mmax= log(cpu_data$mmax,10)

# since chmin <= chmax replace chmax = chmax - chmin.
cpu_data$chmax = cpu_data$chmax - cpu_data$chmin

min_cpu <- as.double(apply(cpu_data,2,min))
max_cpu <- as.double(apply(cpu_data,2,max))

cpu_data = sweep(cpu_data, 2, min_cpu)
cpu_data = sweep(cpu_data, 2, max_cpu - min_cpu, FUN='/')

cpu_data = cbind(cpu_data, perf)

n <- 2^17
d <- ncol(cpu_data) - 1

# Finite interpretable sets (Arbitrary)
U <- interpretable_sets(d,3,8,4)
U = do.call(rbind, U)
```

## Train SVM Model on data.

```{r TSVM}
# NN black-box optimized.
bestmod = nnet(perf ~ ., data=cpu_data, size=3, skip=T,linout=T, decay=1e-4,maxit=1000)
#bestmod$wts = c(-1.12, 0.45, 2.24, 2.51, -1.63, -0.56, 0.43, -1.09, 2.28, -0.1, 1.44, 2.70, 1.24, 0.25, 0.04, -0.11, 0.11, 0.12, -0.1, -0.04, 0.02, 0.46, -2.82, 3.17, 0.39, -1.21, 1.36, 1.42, -1.01, -0.33, 0.3)
# training error
mean((predict(bestmod, cpu_data) - cpu_data$perf)^2)

summary(bestmod)
```


## Code to compute LOF.

```{r}
LOF_EST <- function(d, U, betas, gamma=vector(), n=5000){
  Int_sqr_err = rep(NA, n)
  
  if (length(gamma) == 0)
    gamma = rep(1, nrow(U))
  
  X = gen_unif_mat(n, d)
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  var_f_x = var(f_X)
  
  Int_sqr_err = LOF_EST_cpp(d, X, f_X, var_f_x, U, betas, gamma, n=n)
  
  list(mean=mean(Int_sqr_err), sd=sd(Int_sqr_err) / (sqrt(n)))
}
```

```{r}
X = gen_unif_mat(2^20, d)
colnames(X) <- colnames(cpu_data[,-7])
f_X <- predict(bestmod,X)
var_f_x = var(f_X)[[1]]
var_f_x
```

## Jiang and Owen (2003) Shrinkage approach. 

```{r SQR}
start_time_SQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "cpu_data")
clusterExport(cl, "bestmod")

clusterSetRNGStream(cl)

QRS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(Rcpp)
  library(nnet)
  sourceCpp('QR_code.cpp')
  
  X = gen_unif_mat(n, d)
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  
  QRS_output = QRS_adap(n, U, X, f_X,oracle_shrinkage=FALSE, burn_in=600)
  QRS_output
})

stopCluster(cl)

end_time_SQR <- proc.time() - start_time_SQR
```

## Collect important info.

```{r}
betasQRS_Q = matrix(0, nrow=nrow(U), ncol=num_cores)

for (i in 1:num_cores){
  betasQRS_Q[,i] = QRS_PAR_OUT[[i]][[22]]
}

```

## Compute LOF estimates.

```{r}
LOF_QRS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, U, betas = QRS_PAR_OUT[[j]][[3*i-2]], gamma=QRS_PAR_OUT[[j]][[3*i]])$mean
    })
  list(mean=mean(LOF_est)/var_f_x, sd=sd(LOF_est) / sqrt(num_cores*var_f_x))})
```

## Shrinkage Sensitivity Analysis For QRS

``` {r SA OQR}
output = sensitivity_analysis_QR_ABS(n,d,U,num_cores, cpu_data, betasQRS_Q, LOF_QRS[1,8]$mean,LOF_QRS[2,8]$sd, end_time_SQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/CPU_results_QRS.csv")
```

```{r}
LOF_rate_QRS = lm(log(unlist(LOF_QRS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## RQMC of Ordinary Quasi-Regression

```{r RQR}
start_time_RQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "cpu_data")
clusterExport(cl, "bestmod")

clusterSetRNGStream(cl)

RQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(nnet)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  
  X = sobol(n, d, randomize = "digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  
  RQR_output = QR_adap(n, U, X, f_X)
  RQR_output
})

stopCluster(cl)

end_time_RQR <- proc.time() - start_time_RQR
```

## Collect important info.

```{r}
betasRQR_Q = matrix(0, nrow=nrow(U), ncol=num_cores)

for (i in 1:num_cores){
  betasRQR_Q[,i] = RQR_PAR_OUT[[i]][[15]]
}

```

```{r}
sum(sort(betasRQR_Q[,5][-1]^2, decreasing = T)[1:200]) / sum(betasRQR_Q[,5][-1]^2)
```

## Compute LOF estimates.

```{r}
LOF_RQR = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, U, betas = RQR_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est) / var_f_x, sd=sd(LOF_est) / sqrt(num_cores*var_f_x))})
```

## Shrinkage Sensitivity Analysis For RQR

``` {r SA OQR}
output = sensitivity_analysis_QR_ABS(n,d,U,num_cores, cpu_data, betasRQR_Q, LOF_RQR[1,8]$mean,LOF_RQR[2,8]$sd, end_time_RQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/cpu_results_RQR.csv")
```

```{r}
LOF_rate_RQR = lm(log(unlist(LOF_RQR[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

```{r}
m = 2^16
```


## MARQRSA

```{r RQMC MARQRSA}
start_time_MARQRSA <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "cpu_data")
clusterExport(cl, "bestmod")

clusterSetRNGStream(cl)

MARQRSA_PAR_OUT = clusterEvalQ(cl, 
             {
  library(nnet)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  RQR_output = MAQRSA(m,3,8,4,X,f_X,0.002)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  
  MARQRSA_output = QR_adap(n, U_spar, X, f_X)
  MARQRSA_output[[length(MARQRSA_output) + 1]] = U_spar
  MARQRSA_output
})

stopCluster(cl)

end_time_MARQRSA <- proc.time() - start_time_MARQRSA
```

## Collect important info.

```{r}
betasMARQRSA_Q = list()
U_MARQRSA = list()

for (i in 1:num_cores){
  betasMARQRSA_Q[[i]] = MARQRSA_PAR_OUT[[i]][[15]]
  U_MARQRSA[[i]] = MARQRSA_PAR_OUT[[i]][[17]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQRSA = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, U_MARQRSA[[j]], betas = MARQRSA_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est) / var_f_x, sd=sd(LOF_est) / sqrt(num_cores*var_f_x))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQRSA,num_cores, cpu_data, betasMARQRSA_Q, LOF_MARQRSA[1,8]$mean,LOF_MARQRSA[2,8]$sd, end_time_MARQRSA[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/cpu_results_MARQRSA.csv")
```

```{r}
LOF_rate_MARQRSA = lm(log(unlist(LOF_MARQRSA[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## MARQRNNS

```{r RQMC MARQRNNS}
start_time_MARQRNNS <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "cpu_data")
clusterExport(cl, "bestmod")

clusterSetRNGStream(cl)

MARQRNNS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(nnet)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  MARQRNNS_output = MAQRNNS(m,3,8,4,X,f_X,0.05)
  U_adap <- MARQRNNS_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  
  MARQRNNS_output = QR_adap(n, U_spar, X, f_X)
  MARQRNNS_output[[length(MARQRNNS_output) + 1]] = U_spar
  MARQRNNS_output
})

stopCluster(cl)

end_time_MARQRNNS <- proc.time() - start_time_MARQRNNS
```

## Collect important info.

```{r}
betasMARQRNNS_Q = list()
U_MARQRNNS = list()

for (i in 1:num_cores){
  betasMARQRNNS_Q[[i]] = MARQRNNS_PAR_OUT[[i]][[15]]
  U_MARQRNNS[[i]] = MARQRNNS_PAR_OUT[[i]][[17]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQRNNS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, U_MARQRNNS[[j]], betas = MARQRNNS_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est) / var_f_x, sd=sd(LOF_est) / sqrt(num_cores*var_f_x))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
#var_rate_MARQRNNS = lm(log(vars_MARQRNNS) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQRNNS,num_cores, cpu_data, betasMARQRNNS_Q, LOF_MARQRNNS[1,8]$mean,LOF_MARQRNNS[2,8]$sd, end_time_MARQRNNS[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/cpu_results_MARQRNNS.csv")
```

```{r}
LOF_rate_MARQRNNS = lm(log(unlist(LOF_MARQRNNS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## MARQROS

```{r RQMC MARQROS}
start_time_MARQROS <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "cpu_data")
clusterExport(cl, "bestmod")

clusterSetRNGStream(cl)

MARQROS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(nnet)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  RQR_output = MAQROS(m,3,8,4,X,f_X)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  
  MARQROS_output = QR_adap(n, U_spar, X, f_X)
  MARQROS_output[[length(MARQROS_output) + 1]] = U_spar
  MARQROS_output
})

stopCluster(cl)

end_time_MARQROS <- proc.time() - start_time_MARQROS
```

## Collect important info.

```{r}
betasMARQROS_Q = list()
U_MARQROS = list()

for (i in 1:num_cores){
  betasMARQROS_Q[[i]] = MARQROS_PAR_OUT[[i]][[15]]
  U_MARQROS[[i]] = MARQROS_PAR_OUT[[i]][[17]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQROS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, U_MARQROS[[j]], betas = MARQROS_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est) / var_f_x, sd=sd(LOF_est) / sqrt(num_cores*var_f_x))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQROS,num_cores, cpu_data, betasMARQROS_Q, LOF_MARQROS[1,8]$mean,LOF_MARQROS[2,8]$sd, end_time_MARQROS[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/cpu_results_MARQROS.csv")
```
```{r}
betas_var_true = rep(0,num_cores)

for (i in 1:20){
  betas_var_true[i] = betasMARQROS_Q[[i]][6]
}

var(betas_var_true)
```

```{r}
LOF_rate_MARQROS = lm(log(unlist(LOF_MARQROS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## Results

##### Make Image Less squeezed #####

```{r LOF fits}
plot(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_RQR[1,])), xlab="log(n)", ylab="LOF", ylim=c(-1.8,0.5), col="blue")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_RQR[1,])), col="blue")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_QRS[1,])),col="green")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_QRS[1,])),col="green")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRNNS[1,])), col="purple")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRNNS[1,])), col="purple")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRSA[1,])), col="pink")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQRSA[1,])), col="pink")
points(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQROS[1,])), col="black")
lines(log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)), log(unlist(LOF_MARQROS[1,])), col="black")
legend(9.5, 0.5, legend=c(paste0("RQR (", round(LOF_rate_RQR, 4), ")"), paste0("QRS (", round(LOF_rate_QRS, 4), ")"), paste0("AQRNNS (", round(LOF_rate_MARQRNNS, 4), ")"), paste0("AQRSA (", round(LOF_rate_MARQRSA, 4), ")"),  paste0("AQROS (", round(LOF_rate_MARQROS, 4), ")")),
       col=c("blue", "green", "purple", "pink", "black"), lty=1)
```


```{r runtime}
end_time_SQR[[3]]
end_time_RQR[[3]]
end_time_MARQRNNS[[3]]
end_time_MARQRSA[[3]]
end_time_MARQROS[[3]]
```

# Code not used anymore

## MARQRNS

```{r}
m = 2^13
```

```{r RQMC MARQR}
start_time_MARQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "cpu_data")
clusterExport(cl, "bestmod")

clusterSetRNGStream(cl)

MARQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(nnet)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  MARQR_output = MAQRNS(m,3,8,4,X,f_X,0.05)
  U_adap <- MARQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  
  MARQR_output = QR_adap(n, U_spar, X, f_X)
  MARQR_output[[length(MARQR_output) + 1]] = U_spar
  MARQR_output
})

stopCluster(cl)

end_time_MARQR <- proc.time() - start_time_MARQR
```

## Collect important info.

```{r}
betasMARQR_Q = list()
U_MARQR = list()

for (i in 1:num_cores){
  betasMARQR_Q[[i]] = MARQR_PAR_OUT[[i]][[15]]
  U_MARQR[[i]] = MARQR_PAR_OUT[[i]][[17]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQR = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, U_MARQR[[j]], betas = MARQR_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est) / var_f_x, sd=sd(LOF_est) / sqrt(num_cores*var_f_x))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQR,num_cores, cpu_data, betasMARQR_Q, LOF_MARQR[1,8]$mean,LOF_MARQR[2,8]$sd, end_time_MARQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/cpu_results_MARQR.csv")
```


```{r}
LOF_rate_MARQR = lm(log(unlist(LOF_MARQR[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```

## MARQRLS

```{r RQMC MARQRLS}
start_time_MARQRLS <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "cpu_data")
clusterExport(cl, "bestmod")

clusterSetRNGStream(cl)

MARQRLS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(nnet)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  RQR_output = MAQRLS(m,3,8,4,X,f_X)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  colnames(X) <- colnames(cpu_data[,-7])
  f_X <- predict(bestmod,X)
  
  MARQRLS_output = QR_adap(n, U_spar, X, f_X)
  MARQRLS_output[[length(MARQRLS_output) + 1]] = U_spar
  MARQRLS_output
})

stopCluster(cl)

end_time_MARQRLS <- proc.time() - start_time_MARQRLS
```

## Collect important info.

```{r}
betasMARQRLS_Q = list()
U_MARQRLS = list()

for (i in 1:num_cores){
  betasMARQRLS_Q[[i]] = MARQRLS_PAR_OUT[[i]][[15]]
  U_MARQRLS[[i]] = MARQRLS_PAR_OUT[[i]][[17]]
}

```

## Compute LOF estimates.

```{r}
LOF_MARQRLS = sapply(1:8, FUN=function(i){
  LOF_est = sapply(1:num_cores, FUN=function(j){
    LOF_EST(d, U_MARQRLS[[j]], betas = MARQRLS_PAR_OUT[[j]][[2*i-1]])$mean
    })
  list(mean=mean(LOF_est) / var_f_x, sd=sd(LOF_est) / sqrt(num_cores*var_f_x))})
```

## Senstivity Analysis For RQR

``` {r SA OQR}
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQRLS,num_cores, cpu_data, betasMARQRLS_Q, LOF_MARQRLS[1,8]$mean,LOF_MARQRLS[2,8]$sd, end_time_MARQRLS[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/cpu_results_MARQRLS.csv")
```

```{r}
LOF_rate_MARQRLS = lm(log(unlist(LOF_MARQRLS[1,])) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
```