---
title: "Email Rcpp"
author: "Ambrose Emmett-Iwaniw"
date: "16/8/2023"
output: pdf_document
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = TRUE)
library(kernlab)
library(gbm)
data("spam")
library(qrng)
library(Rcpp)
library(parallel)
setwd('C:/Users/arsemmet/Desktop/QR Paper Code')
sourceCpp('QR_code.cpp')
sourceCpp('Adaptive_QR_helper.cpp')
source('sensitivity_analysis.R')
source('data_preparation.R') 
#source("C:/Users/arsemmet/Desktop/QR Paper Code/scrambled_sobol.R")
set.seed(20669099)
```

# Training the Boosted Tree Model.

## Data Preparation
```{r DP}
# Data Preparation.
Type <- spam$type
Type = as.numeric(Type) - 1
spam_data <- spam[,-58]

min_spam <- as.double(apply(spam_data,2,min))
max_spam <- as.double(apply(spam_data,2,max))

spam_data = sweep(spam_data, 2, min_spam)
spam_data = sweep(spam_data, 2, max_spam - min_spam, FUN='/')

spam_data = cbind(spam_data, Type)

n <- 2^16
n_steps = log2(n) - log2(2^10) + 1
m <- 2^16
d <- ncol(spam_data) - 1
```

## Data Preparation
```{r DP}
# Finite interpretable sets (Arbitrary)
U <- interpretable_poly_sets(d,2,10,5)
U = do.call(rbind, U)
nrow(U)
```

## Splitting Data
```{r}
rnd_sample <- sample(1:nrow(spam))

spam_train <- spam_data[rnd_sample[1:3200],]
spam_valid <- spam_data[rnd_sample[3201:4000],]
spam_test <- spam_data[rnd_sample[4001:4601],]
```

## Fit a Boosted Tree Model on the training data.
```{r FGBM}
gbm_spam <- gbm(Type ~ . , data = spam_train ,n.trees = 1000,
                interaction.depth = 6, distribution = "bernoulli", n.minobsinnode = 10)

# summary(gbm_spam) #Summary gives a table of Variable Importance and a plot of Variable Importance
```
## Finding optimal number of trees using validation set.
```{r}
n.trees = seq(from=100, to=1000, by=10) #no of trees-a vector of 100 values

#Generating a Prediction matrix for each Tree
predmatrix <- predict(gbm_spam, spam_valid, n.trees = n.trees,type = "response")
predmatrix = predmatrix >= 0.5
predmatrix = 1*predmatrix
dim(predmatrix)

#Calculating Validation Error curve.
valid.error <- with(spam_valid,apply(predmatrix!=Type,2,mean))
head(valid.error) #contains the validation error for each of the 100 trees averaged

#Plotting the test error vs number of trees

plot(n.trees , valid.error , pch=19,col="blue",xlab="Number of Trees",ylab="Test Error", main = "Perfomance of Boosting on Test Set")

which.min(valid.error)
valid.error[21]
```
Based on the results of validation set. optimal number of trees is 300.

## The training, validation and test error for Boosted tree model.
```{r}
opt.tree <- 300
#Generating a Prediction 
pred_train <- predict(gbm_spam, spam_train, n.trees = opt.tree, type = "response")
pred_train = 1*(pred_train >= 0.5)
#Calculating Validation Error curve.
train_error <- with(spam_train,mean(pred_train!=Type))
train_error

pred_valid <- predict(gbm_spam, spam_valid, n.trees = opt.tree, type = "response")
pred_valid = 1*(pred_valid >= 0.5)
#Calculating Validation Error curve.
valid_error <- with(spam_valid,mean(pred_valid!=Type))
valid_error

pred_test <- predict(gbm_spam, spam_test, n.trees = opt.tree, type = "response")
pred_test = 1*(pred_test >= 0.5)
#Calculating Validation Error curve.
test_error <- with(spam_test,mean(pred_test !=Type))
test_error
```

training error: $1.22\%$. Validation error: $3.5\%$. Test error: $5.66\%$.

## Variable importance.

```{r}
summary.gbm(gbm_spam)
```

## Code to compute LOF.

```{r}
LOF_EST <- function(d, U, betas, gamma=vector(), n=5000){
  Int_sqr_err = rep(NA, n)
  
  if (length(gamma) == 0)
    gamma = rep(1, nrow(U))
  
  X = gen_unif_mat(n, d)
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  var_f_x = var(f_X)
  
  Int_sqr_err = LOF_EST_cpp(d, X, f_X, var_f_x, U, betas, gamma, n=n)
  
  list(mean=mean(Int_sqr_err) / var_f_x, sd=sd(Int_sqr_err) / (sqrt(n*var_f_x)), ISE_mean=mean(Int_sqr_err),  ISE_sd=sd(Int_sqr_err) / sqrt(n))
}
```

```{r QR, eval=FALSE, include=FALSE}
start_time_QR <- proc.time()
Q <- 15

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "spam_data")
clusterExport(cl, "gbm_spam")
clusterExport(cl, "opt.tree")

clusterSetRNGStream(cl)

QR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(kernlab)
  library(gbm)
  library(Rcpp)
  library(qrng)
  sourceCpp('C:/Users/ambro/Desktop/QR Paper Code/QR_code.cpp')
  
  X = gen_unif_mat(n, d)
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  
  QR_output = QR_adap(n, U, X, f_X)
  QR_output
})

stopCluster(cl)

end_time_QR <- proc.time() - start_time_QR
```

## Jiang and Owen (2003) Shrinkage approach. 

```{r SQR}
start_time_SQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "spam_data")
clusterExport(cl, "gbm_spam")
clusterExport(cl, "opt.tree")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

QRS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(gbm)
  library(Rcpp)
  sourceCpp('QR_code.cpp')
  
  X = gen_unif_mat(n, d)
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  
  QRS_output = QRS_email(n, U, X, f_X,oracle_shrinkage=FALSE)
  
   # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U, betas = QRS_output[[3*i-2]], gamma=QRS_output[[3*i]])$mean
  })
  
  QRS_output[[length(QRS_output) + 1]] = LOF_val
  QRS_output
})

stopCluster(cl)

end_time_SQR <- proc.time() - start_time_SQR
```

## Collect important info.

```{r}
betasQRS_Q = matrix(0, nrow=nrow(U), ncol=num_cores)
LOF_QRS = list()
para_indx = n_steps * 3 - 2

for (i in 1:num_cores){
  betasQRS_Q[,i] = QRS_PAR_OUT[[i]][[para_indx]]
  LOF_QRS[[i]] = QRS_PAR_OUT[[i]][[3*n_steps+1]]
}

LOF_QRS = do.call(rbind, LOF_QRS)

```

## Shrinkage Sensitivity Analysis For QRS

``` {r SA OQR}
LOF_QRS_mean = mean(LOF_QRS[,n_steps]) 
LOF_QRS_sd = sd(LOF_QRS[,n_steps]) / sqrt(num_cores)
output = sensitivity_analysis_QR_ABS(n,d,U,num_cores, spam_data, betasQRS_Q, LOF_QRS_mean,LOF_QRS_sd, end_time_SQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Email_results_QRS.csv")
```

```{r}
LOF_rate_QRS = lm(log(LOF_QRS[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## RQMC of Ordinary Quasi-Regression

```{r RQR}
start_time_RQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "spam_data")
clusterExport(cl, "gbm_spam")
clusterExport(cl, "opt.tree")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

RQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(kernlab)
  library(gbm)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  
  X = sobol(n, d, randomize = "digital.shift")
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  
  RQR_output = QR_email(n, U, X, f_X)
  
  # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U, betas = RQR_output[[2*i-1]])$mean
  })
  
  RQR_output[[length(RQR_output) + 1]] = LOF_val
  RQR_output
})

stopCluster(cl)

end_time_RQR <- proc.time() - start_time_RQR
```

## Collect important info.

```{r}
betasRQR_Q = matrix(0, nrow=nrow(U), ncol=num_cores)
LOF_RQR = list()
para_indx = n_steps * 2 - 1

for (i in 1:num_cores){
  betasRQR_Q[,i] = RQR_PAR_OUT[[i]][[para_indx]]
  LOF_RQR[[i]] = RQR_PAR_OUT[[i]][[2*n_steps+1]]
}

LOF_RQR = do.call(rbind, LOF_RQR)
```

## Shrinkage Sensitivity Analysis For RQR

``` {r SA OQR}
LOF_RQR_mean = mean(LOF_RQR[,n_steps]) 
LOF_RQR_sd = sd(LOF_RQR[,n_steps]) / sqrt(num_cores)
output = sensitivity_analysis_QR_ABS(n,d,U,num_cores, spam_data, betasRQR_Q, LOF_RQR_mean,LOF_RQR_sd, end_time_RQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Email_results_RQR.csv")
```

```{r}
LOF_rate_RQR = lm(log(LOF_RQR[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## MARQRNS

```{r RQMC MARQR}
start_time_MARQR <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "spam_data")
clusterExport(cl, "gbm_spam")
clusterExport(cl, "opt.tree")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

MARQR_PAR_OUT = clusterEvalQ(cl, 
             {
  library(kernlab)
  library(gbm)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  
  RQR_output = MAQRNS(m,2,10,5,X,f_X,0.00001)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  
  MARQR_output = QR_adap(n, U_spar, X, f_X)
  MARQR_output[[length(MARQR_output) + 1]] = U_spar
  
  # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U_spar, betas = MARQR_output[[2*i-1]])$mean
  })
  
  MARQR_output[[length(MARQR_output) + 1]] = LOF_val
  
  MARQR_output
})

stopCluster(cl)

end_time_MARQR <- proc.time() - start_time_MARQR
```

## Collect important info.

```{r}
betasMARQR_Q = list()
U_MARQR = list()
LOF_MARQR = list()

for (i in 1:num_cores){
  betasMARQR_Q[[i]] = MARQR_PAR_OUT[[i]][[2*n_steps - 1]]
  U_MARQR[[i]] = MARQR_PAR_OUT[[i]][[2*n_steps+1]]
  LOF_MARQR[[i]] = MARQR_PAR_OUT[[i]][[2*n_steps+2]]
}

LOF_MARQR = do.call(rbind, LOF_MARQR)

```

## Senstivity Analysis For RQR

``` {r SA OQR}
LOF_MARQR_mean = mean(LOF_MARQR[,n_steps]) 
LOF_MARQR_sd = sd(LOF_MARQR[,n_steps]) / sqrt(num_cores)
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQR,num_cores, spam_data, betasMARQR_Q, LOF_MARQR_mean,LOF_MARQR_sd, end_time_MARQR[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Email_results_MARQR.csv")
```

```{r}
LOF_rate_MARQR = lm(log(LOF_MARQR[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## MARQRSA

```{r RQMC MARQRSA}
start_time_MARQRSA <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "spam_data")
clusterExport(cl, "gbm_spam")
clusterExport(cl, "opt.tree")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

MARQRSA_PAR_OUT = clusterEvalQ(cl, 
             {
  library(kernlab)
  library(gbm)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  RQR_output = MAQRSA(m,2,10,5,X,f_X,0.1)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  
  MARQRSA_output = QR_adap(n, U_spar, X, f_X)
  MARQRSA_output[[length(MARQRSA_output) + 1]] = U_spar
  
  # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U_spar, betas = MARQRSA_output[[2*i-1]])$mean
  })
  
  MARQRSA_output[[length(MARQRSA_output) + 1]] = LOF_val
  MARQRSA_output
})

stopCluster(cl)

end_time_MARQRSA <- proc.time() - start_time_MARQRSA
```

## Collect important info.

```{r}
betasMARQRSA_Q = list()
U_MARQRSA = list()
LOF_MARQRSA = list()

for (i in 1:num_cores){
  betasMARQRSA_Q[[i]] = MARQRSA_PAR_OUT[[i]][[2*n_steps - 1]]
  U_MARQRSA[[i]] = MARQRSA_PAR_OUT[[i]][[2*n_steps+1]]
  LOF_MARQRSA[[i]] = MARQRSA_PAR_OUT[[i]][[2*n_steps+2]]
}

LOF_MARQRSA = do.call(rbind, LOF_MARQRSA)

```

## Senstivity Analysis For RQR

``` {r SA OQR}
LOF_MARQRSA_mean = mean(LOF_MARQRSA[,n_steps]) 
LOF_MARQRSA_sd = sd(LOF_MARQRSA[,n_steps]) / sqrt(num_cores)
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQRSA,num_cores, spam_data, betasMARQRSA_Q, LOF_MARQRSA_mean,LOF_MARQRSA_sd, end_time_MARQRSA[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Email_results_MARQRSA.csv")
```

```{r}
LOF_rate_MARQRSA = lm(log(LOF_MARQRSA[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## MARQROS

```{r RQMC MARQROS}
start_time_MARQROS <- proc.time()

num_cores = detectCores()
cl <- makeCluster(num_cores)

clusterExport(cl, "n")
clusterExport(cl, "m")
clusterExport(cl, "d")
clusterExport(cl, "U")
clusterExport(cl, "spam_data")
clusterExport(cl, "gbm_spam")
clusterExport(cl, "opt.tree")
clusterExport(cl, "n_steps")
clusterExport(cl, "LOF_EST")

clusterSetRNGStream(cl)

MARQROS_PAR_OUT = clusterEvalQ(cl, 
             {
  library(kernlab)
  library(gbm)
  library(Rcpp)
  library(qrng)
  sourceCpp('QR_code.cpp')
  sourceCpp('Adaptive_QR_helper.cpp')
  
  X = sobol(m,d, randomize="digital.shift")
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  RQR_output = MAQROS(m,2,10,5,X,f_X)
  U_adap <- RQR_output
  U_spar = do.call(rbind, U_adap)
  
  U_comb <- rbind(U_spar,U)
  sel_basis = duplicated(U_comb)[-(1:nrow(U_spar))]
  U_spar = U[sel_basis,]
  
  X = sobol(n, d, randomize = "digital.shift")
  X_df = as.data.frame(X)
  colnames(X_df) = colnames(spam_data)[-58]
  f_X <- predict(gbm_spam, X_df, n.trees=opt.tree, type="response")
  
  MARQROS_output = QR_adap(n, U_spar, X, f_X)
  MARQROS_output[[length(MARQROS_output) + 1]] = U_spar
  
  # Compute LOF estimate.
  LOF_val = sapply(1:n_steps, FUN=function(i){
    LOF_EST(d, U_spar, betas = MARQROS_output[[2*i-1]])$mean
  })
  
  MARQROS_output[[length(MARQROS_output) + 1]] = LOF_val
  MARQROS_output
})

stopCluster(cl)

end_time_MARQROS <- proc.time() - start_time_MARQROS
```

## Collect important info.

```{r}
betasMARQROS_Q = list()
U_MARQROS = list()
LOF_MARQROS = list()

for (i in 1:num_cores){
  betasMARQROS_Q[[i]] = MARQROS_PAR_OUT[[i]][[2*n_steps - 1]]
  U_MARQROS[[i]] = MARQROS_PAR_OUT[[i]][[2*n_steps+1]]
  LOF_MARQROS[[i]] = MARQROS_PAR_OUT[[i]][[2*n_steps+2]]
}

LOF_MARQROS = do.call(rbind, LOF_MARQROS)

```

## Senstivity Analysis For RQR

``` {r SA OQR}
LOF_MARQROS_mean = mean(LOF_MARQROS[,n_steps]) 
LOF_MARQROS_sd = sd(LOF_MARQROS[,n_steps]) / sqrt(num_cores)
#var_rate_MARQR = lm(log(vars_MARQR) ~ log(c(2^10,2^11, 2^12, 2^13, 2^14, 2^15, 2^16, 2^17)))$coefficients[[2]]
output = sensitivity_analysis_MARQR_ABS(n,d,U_MARQROS,num_cores, spam_data, betasMARQROS_Q, LOF_MARQROS_mean, LOF_MARQROS_sd, end_time_MARQROS[[3]])

write.csv(output, file="C:/Users/arsemmet/Desktop/QR Paper Code/Email_results_MARQROS.csv")
```

```{r}
LOF_rate_MARQROS = lm(log(LOF_MARQROS[1,]) ~ log(2^seq(10,log2(n),1)))$coefficients[[2]]
```

## Results

```{r LOF fits}
LOF_x_axis = log(2^seq(10,log2(n),1))
plot(LOF_x_axis, log(unlist(LOF_RQR[1,])), xlab="log(n)", ylab="LOF", ylim=c(-5.5,5.5), col="blue")
lines(LOF_x_axis, log(unlist(LOF_RQR[1,])), col="blue")
points(LOF_x_axis, log(unlist(LOF_QRS[1,])),col="green")
lines(LOF_x_axis, log(unlist(LOF_QRS[1,])),col="green")
points(LOF_x_axis, log(unlist(LOF_MARQR[1,])), col="purple")
lines(LOF_x_axis, log(unlist(LOF_MARQR[1,])), col="purple")
points(LOF_x_axis, log(unlist(LOF_MARQRSA[1,])), col="pink")
lines(LOF_x_axis, log(unlist(LOF_MARQRSA[1,])), col="pink")
points(LOF_x_axis, log(unlist(LOF_MARQROS[1,])), col="black")
lines(LOF_x_axis, log(unlist(LOF_MARQROS[1,])), col="black")
legend(10, 5.5, legend=c(paste0("RQR (", round(LOF_rate_RQR, 4), ")"), paste0("QRS (", round(LOF_rate_QRS, 4), ")"), paste0("MARQR (", round(LOF_rate_RQRS, 4), ")"), paste0("MARQRSA (", round(LOF_rate_QRRS, 4), ")"),  paste0("MARQRLS (", round(LOF_rate_MARQROS, 4), ")")),
       col=c("blue", "green", "purple", "pink", "black"), lty=1)
```


```{r runtime}
end_time_SQR[[3]]
end_time_RQR[[3]]
end_time_MARQR[[3]]
end_time_MARQRSA[[3]]
end_time_MARQRLS[[3]]
```